### 2019-09-13 scache/tii/tex/conclusion.tex
Fix the typo provided by JungleX
Revision

\section{Conclusion}\label{conclusion}
In this paper, we present SCache, a cross-framework shuffle optimization for DAG computing frameworks. 
SCache decouples the shuffle from computing tasks and leverages memory to store shuffle data. 
By task pre-scheduling and shuffle data pre-fetching with application context, SCache significantly mitigates the shuffle overhead. 
%  {\color{red}
%  Our implementation with Spark and evaluations show that SCache can provide a promising speedup to the DAG framework. 
%  }
{\color{black}
% Our evaluations on Spark and Hadoop MapReduce with SCache show that SCache can provide a promising speedup. 
% The benchmark using in evaluations covers the most situations of industrial big-data analysis.
The evaluations show that SCache can provide a promising speedup in both traditional and industrial big-data workloads. 
Furthermore, we propose \textit{Framework Resources Quantification} (FRQ) model to assist in analyzing shuffle process of DAG computing frameworks. 
% At last, we evaluate the SCache shuffle optimization by the FRQ model.
% Therefore, with the shared defects of shuffle among different frameworks, we believe that the optimization of SCache is general and easy to be adapted. 
}

>>>>

\section{Conclusion}\label{conclusion}
In this paper, we present SCache, a plug-in shuffle optimization for DAG computing frameworks. 
% SCache decouples the shuffle from computing tasks and leverages memory to store shuffle data. 
By task pre-scheduling and shuffle data pre-fetching with application context, SCache decouples the shuffle from computing tasks and mitigates the shuffle overhead. 
%  {\color{red}
%  Our implementation with Spark and evaluations show that SCache can provide a promising speedup to the DAG framework. 
%  }
{\color{black}
% Our evaluations on Spark and Hadoop MapReduce with SCache show that SCache can provide a promising speedup. 
% The benchmark using in evaluations covers the most situations of industrial big data analysis.
We also propose \textit{Framework Resources Quantification} (FRQ) model to evaluate the shuffle process of DAG computing frameworks. 
The evaluations show that SCache can provide a promising speedup in industrial production workloads. 
% At last, we evaluate the SCache shuffle optimization by the FRQ model.
% Therefore, with the shared defects of shuffle among different frameworks, we believe that the optimization of SCache is general and easy to be adapted. 
}

### 2019-09-13 scache/tii/tex/evaluation.tex
Revision

\subsection{Setup}\label{stepup}
% We modified Spark to enable shuffle optimization of SCache as a representative.
We use Spark version 1.6.2 and Hadoop MapReduce version 2.8.5.
The shuffle configuration of Spark is set to the default\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}. 
We run the experiments on a 50-node m4.xlarge cluster on Amazon EC2\footnote{http://aws.amazon.com/ec2/}. 
Each node has 16GB memory and 4 CPUs.
The network bandwidth each node is about 300 Mbps.
% The network bandwidth provided by Amazon is insufficient. 
% Our evaluations reveal the bandwidth is only about 300 Mbps.
%  (see Figure \ref{fig:util}).

@@

As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase and the shuffle phase and the reduce phase start simultaneously. The beginning part of reduce phase needs to wait for network transfer because a large amount of shuffle data reaches the network bottleneck. This causes the CPU resources to be idle. 
On the other hand, in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache starts pre-fetching in the map phase. This avoids the reduce phase waiting for the shuffle data. Furthermore, pre-fetching utilizes the idle I/O throughput in the map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after decoupling shuffle, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
}

@@

\subsection{The FRQ Model Evaluation}\label{model_evaluation}
% To evaluate the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster; (b) 4 in-house nodes cluster with 128GB memory and 32 cores per node.
% We run the Terasort as an experimental application on a Hadoop MapReduce framework.
% We deployed Hadoop with SCache and without SCache in both environments.
To evaluate the FRQ model, we run Terasort with Hadoop MapReduce with two different environments and use the FRQ to model the jobs.
% The workload is from 16 GB to 64 GB. 
% \(D\) and \(N\) are set according to the application parameters. We set \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) according to the environment.
The parameters \(D\), \(N\), \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) are set according to the application and the environment.
We set \(K\) to 0.5 and 0.6 since SCache alleviates the defect on the reduce phase
Table \ref{table1} shows the results in the in-house environment.
% The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are according to Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively. 
While enabling SCache, Terasort satisfies the situation in Figure \ref{fig:model_basic} (\(V_{Map} \times R \ge V_{Shuffle}\)). 
% thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}.
While without SCache, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tmap}).
\(ExpT_{Job}\) represents the actual experiment job times and
\(Error\) represents the error between \(T_{Job}\) and \(ExpT_{Job}\). 
% The formula of \(Error\) is:
% \begin{equation}
% 	\label{equation_error}
% 	\begin{aligned}
% 		Error &= \frac{ExpT_{Job} - T_{Job}}{T_{Job}}
% 	\end{aligned}
% \end{equation}
Table \ref{table2} shows the results in Amazon EC2 environment.
% \;\(V_{Map}, V_{Shuffle},\) and \(V_{Reduce}\) are modified because of the different hardware devices.
% We set K to the same value.
% The formulas in the table are all the same except \(T_{P\_Shuffle}\).
In this environment, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache2} (\(V_{Map} \times R < V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle2}. 
% In the previous case, \(T_{P\_Shuffle}\) is still equal to \(T_{Shuffle}\).

@@

\begin{table*}
\centering
\scalebox{0.95}{
	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
	\hline
	&
	\(D\) &	
	\(R\) &	
	\(N\) &	
	\(V_{Map}\) &	
	\(V_{Reduce}\) &	
	\(V_{Shuffle}\) &	
	\(K\) &	
	\(T_{Map}\) &	
	\(T_{Shuffle}\) &	
	\(T_{P\_Shuffle}\) &
	\(T_{Reduce}\) & 
	\(T_{Job}\) & 
	\(Exp T_{Job}\) &
	\(Error\)\\

	\hline
	% & 16	& 1	& 2 &	0.65 &	1 &	0.47 &	0.5 &	24.62 &		34.04	 &	21.73 &	26.87 &	51.48	& 55  &		6.39\% \\
	SCache
	& 32	& 1	& 4 &	0.65 &	1 &	0.47 &	0.5 &	49.23 &		68.09	 &	31.16 &	47.58 &	96.81	& 104 & 	6.91\% \\
	& 48	& 1	& 6 &	0.65 &	1 &	0.47 &	0.5 &	73.85 &		102.13 &	40.59 &	68.29 &	142.14	& 151 & 	5.87\% \\
	& 64	& 1	& 8 &	0.65 &	1 &	0.47 &	0.5 &	98.46 &		136.17 &	50.02 &	89.01 &	187.47	& 193 & 	2.87\% \\
	\hline
	% & 16	& 1 & 2 &	0.65 &	1 &	0.47 &	0.6 &	24.62 &		34.04	&	34.04	&	36.43	&	61.04	&	73	&	16.38\%	\\
	Legacy
	& 32	& 1 & 4 &	0.65 &	1 &	0.47 &	0.6 &	49.23 &		68.09	&	68.09	&	72.85	&	122.08	&	135	&	9.57\%	\\
	& 48	& 1 & 6 &	0.65 &	1 &	0.47 &	0.6 &	73.85 &		102.13	&	102.13	&	109.28	&	183.12	&	188	&	2.59\%	\\
	& 64	& 1 & 8 &	0.65 &	1 &	0.47 &	0.6 &	98.46 &		136.17	&	136.17	&	145.70	&	244.16	&	249	&	1.94\%	\\
	\hline
	\end{tabular}
}
\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\caption{\color{black}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
\label{table1}
\end{table*}

@@

\begin{table*}
\centering
\scalebox{0.95}{
	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
	\hline
	&
	\(D\) &	
	\(R\) &	
	\(N\) &	
	\(V_{Map}\) &	
	\(V_{Reduce}\) &	
	\(V_{Shuffle}\) &	
	\(K\) &	
	\(T_{Map}\) &	
	\(T_{Shuffle}\) &	
	\(T_{P\_Shuffle}\) &
	\(T_{Reduce}\) & 
	\(T_{Job}\) & 
	\(Exp T_{Job}\) &
	\(Error\)\\

	\hline
	& 128	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	111.30 &	91.43	&	18.29	&	96.81	&	208.12	&	232	&	10.29\%	\\
	SCache
	& 256	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	222.61 &	182.86	&	36.57	&	193.63	&	416.24	&	432	&	3.65\%	\\
	& 384	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	333.91 &	274.29	&	54.86	&	290.44	&	624.36	&	685 &	8.85\%	\\
	% & 512	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	445.22 &	365.71	&	91.43	&			&	841.62	&	1135 &	25.85\%	\\
	\hline
	& 128	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	111.30 &	91.43	&	91.43	&	142.53	&	253.83	&	266 &	4.57\%	\\
	Legacy
	& 256	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	222.61 &	182.86	&	182.86	&	285.06	&	507.67	&	524 &	3.12\%	\\
	& 384	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	333.91 &	274.29	&	274.29	&	427.59	&	761.50	&	776 &	1.87\%	\\
	% & 512	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	445.22 &	365.71	&	365.71	&	588.40	&	1033.62	&	1312 &	21.22\%	\\

	\hline
	\end{tabular}
}
\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\caption{\color{black}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
\label{table2}
\end{table*}

>>>>

\subsection{Setup}\label{stepup}
% We modified Spark to enable shuffle optimization of SCache as a representative.
We use Spark version 1.6.2 and Hadoop MapReduce version 2.8.5.
The shuffle configuration of Spark is set to the default\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}. 
We run the experiments on a 50-node m4.xlarge cluster on Amazon EC2.
% \footnote{http://aws.amazon.com/ec2/}. 
Each node has 16GB memory and 4 CPUs.
The network bandwidth each node is about 300 Mbps.
% The network bandwidth provided by Amazon is insufficient. 
% Our evaluations reveal the bandwidth is only about 300 Mbps.
%  (see Figure \ref{fig:util}).

@@

As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache starts shuffle and reduce simultaneously.
% writes intermediate data locally in the map phase and the shuffle phase and the reduce phase start simultaneously.
The beginning part of reduce phase needs to wait for network transfer because a large amount of shuffle data reaches the network bottleneck.
This causes the CPU resources to be idle. 
On the other hand, in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache decouples shuffle from reduce and starts pre-fetching in the map phase.
% This avoids the reduce phase waiting for the shuffle data.
SCache utilizes the idle I/O throughput in the map phase.
As shown in Figure \ref{fig:hadoop_terasort_time}, after decoupling, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
}

@@

\subsection{The FRQ Model Evaluation}\label{model_evaluation}
% To evaluate the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster; (b) 4 in-house nodes cluster with 128GB memory and 32 cores per node.
% We run the Terasort as an experimental application on a Hadoop MapReduce framework.
% We deployed Hadoop with SCache and without SCache in both environments.
To evaluate the FRQ model, we run Terasort with Hadoop MapReduce with two different environments.
%  and use the FRQ to model the jobs.
% The workload is from 16 GB to 64 GB. 
% \(D\) and \(N\) are set according to the application parameters. We set \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) according to the environment.
The parameters \(D\), \(N\), \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) are set according to the application and the environment.
We set \(K\) to 0.5 and 0.6 since SCache alleviates the defect on the reduce phase
Table \ref{table1} shows the results in the in-house environment.
% The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are according to Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively. 
While enabling SCache, Terasort satisfies the situation in Figure \ref{fig:model_basic} (\(V_{Map} \times R \ge V_{Shuffle}\)). 
% thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}.
While without SCache, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tmap}).
\(ExpT_{Job}\) represents the actual experiment job times and
\(Error\) represents the error between \(T_{Job}\) and \(ExpT_{Job}\). 
% The formula of \(Error\) is:
% \begin{equation}
% 	\label{equation_error}
% 	\begin{aligned}
% 		Error &= \frac{ExpT_{Job} - T_{Job}}{T_{Job}}
% 	\end{aligned}
% \end{equation}
Table \ref{table2} shows the results in Amazon EC2.
% \;\(V_{Map}, V_{Shuffle},\) and \(V_{Reduce}\) are modified because of the different hardware devices.
% We set K to the same value.
% The formulas in the table are all the same except \(T_{P\_Shuffle}\).
In this environment, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache2} (\(V_{Map} \times R < V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle2}. 
% In the previous case, \(T_{P\_Shuffle}\) is still equal to \(T_{Shuffle}\).

@@

\begin{table*}
\centering
\scalebox{0.85}{
	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
	\hline
	&
	\(D\) &	
	\(R\) &	
	\(N\) &	
	\(V_{Map}\) &	
	\(V_{Reduce}\) &	
	\(V_{Shuffle}\) &	
	\(K\) &	
	\(T_{Map}\) &	
	\(T_{Shuffle}\) &	
	\(T_{P\_Shuffle}\) &
	\(T_{Reduce}\) & 
	\(T_{Job}\) & 
	\(Exp T_{Job}\) &
	\(Error\)\\

	\hline
	% & 16	& 1	& 2 &	0.65 &	1 &	0.47 &	0.5 &	24.62 &		34.04	 &	21.73 &	26.87 &	51.48	& 55  &		6.39\% \\
	SCache
	& 32 GB & 1	& 4 &	0.65 GB/s &	1 GB/s  &	0.47 GB/s &	0.5 &	49.23 &		68.09  s &	31.16 s &	47.58 s &	96.81	s & 104 s & 	6.91\% \\
	& 48 GB	& 1	& 6 &	0.65 GB/s &	1 GB/s  &	0.47 GB/s &	0.5 &	73.85 &		102.13 s &	40.59 s &	68.29 s &	142.14	s & 151 s & 	5.87\% \\
	& 64 GB	& 1	& 8 &	0.65 GB/s &	1 GB/s  &	0.47 GB/s &	0.5 &	98.46 &		136.17 s &	50.02 s &	89.01 s &	187.47	s & 193 s & 	2.87\% \\
	\hline
	% & 16	& 1 & 2 &	0.65 GB/s &	1 &	0.47 &	0.6 &	24.62 &		34.04	&	34.04	&	36.43	&	61.04	&	73	&	16.38\%	\\
	Legacy
	& 32 GB	& 1 & 4 &	0.65 GB/s &	1 GB/s &	0.47 GB/s &	0.6 &	49.23 s &		68.09 s &	68.09 s		&	72.85	s &	122.08 s	&	135 s	&	9.57\%	\\
	& 48 GB	& 1 & 6 &	0.65 GB/s &	1 GB/s &	0.47 GB/s &	0.6 &	73.85 s &		102.13 s &	102.13 s	&	109.28	s &	183.12 s	&	188 s	&	2.59\%	\\
	& 64 GB	& 1 & 8 &	0.65 GB/s &	1 GB/s &	0.47 GB/s &	0.6 &	98.46 s &		136.17 s &	136.17 s	&	145.70	s &	244.16 s	&	249 s	&	1.94\%	\\
	\hline
	\end{tabular}
}
% \(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\caption{\color{black}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
\label{table1}
\end{table*}

@@

\begin{table*}
\centering
\scalebox{0.85}{
	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
	\hline
	&
	\(D\) &	
	\(R\) &	
	\(N\) &	
	\(V_{Map}\) &	
	\(V_{Reduce}\) &	
	\(V_{Shuffle}\) &	
	\(K\) &	
	\(T_{Map}\) &	
	\(T_{Shuffle}\) &	
	\(T_{P\_Shuffle}\) &
	\(T_{Reduce}\) & 
	\(T_{Job}\) & 
	\(Exp T_{Job}\) &
	\(Error\)\\

	\hline
	SCache
	& 128 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.5 &	111.30 &	91.43	&	18.29	&	96.81	&	208.12	&	232	&	10.29\%	\\
	& 256 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.5 &	222.61 &	182.86	&	36.57	&	193.63	&	416.24	&	432	&	3.65\%	\\
	& 384 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.5 &	333.91 &	274.29	&	54.86	&	290.44	&	624.36	&	685 &	8.85\%	\\
	% & 512	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.5 &	445.22 &	365.71	&	91.43	&			&	841.62	&	1135 &	25.85\%	\\
	\hline
	Legacy
	& 128 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.6 &	111.30 s &	91.43	s &	91.43	s &	142.53	s &	253.83	s &	266 s &	4.57\%	\\
	& 256 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.6 &	222.61 s &	182.86	s &	182.86	s &	285.06	s &	507.67	s &	524 s &	3.12\%	\\
	& 384 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.6 &	333.91 s &	274.29	s &	274.29	s &	427.59	s &	761.50	s &	776 s &	1.87\%	\\
	% & 512	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	445.22 &	365.71	&	365.71	&	588.40	&	1033.62	&	1312 &	21.22\%	\\

	\hline
	\end{tabular}
}
% \(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\caption{\color{black}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
\label{table2}
\end{table*}

### 2019-09-13 scache/tii/tex/impl.tex
Revision

% After a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API to move all the blocks out of framework worker through memory copy and release the slot immediately.
After a map task finishes computing, the shuffle writes in the map task is modified to use SCache API to memory copy all shuffle blocks to the SCache worker reserved memory.
% After that, the slot will be released (without being blocked on disk operations).
The SCahce records the block ID and the size and sends them to the master.
% When a block of the map output is received, the SCache worker will send the block ID and the size to the master.
% If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
If the collected shuffle blocks reach a threshold, the SCache co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks.
After pre-scheduling, SCahce workers start pre-fetching shuffle blocks according to the assignment from the master.
To enforce the DAG framework to assign tasks according to the SCache pre-scheduled results, we also insert some lines of codes in the framework scheduler.
}
% After modification, the DAG scheduler consults SCache co-scheduler to get the preferred location for each task.

@@

\subsubsection{All-or-Nothing Constraint}
% This acceleration of in-memory cache of a single task is necessary but insufficient for a shorter stage completion time. 
{\color{blue}
% Based on the observation in Section \ref{multi}, in most cases one single stage contains multi-rounds of tasks.
% Both experience and DAG framework manuals (e.g., Hadoop and Spark) recommend that multi-round execution of each stage will benefit the performance of applications.
As discussed in the observation in Subsection \ref{observation}, it is common to have multi-round execution of each stage. 
If one of the task in a round missed a memory cache, the re-fetch overhead will become a bottleneck and then slow down the whole stage. 
% If one task missed a memory cache and exceeded the original bottleneck of this round, that task might become the new bottleneck and then slow down the whole stage. 
% PACMan \cite{pacman} has also proved that for multi-round stage/job, the completion time improves in steps when $n\times number\ of\ tasks\ in\ one\ round$ of tasks have data cached simultaneously. 
% Therefore, the cached shuffle blocks need to match the demand of all tasks in one running round at least.
}
Therefore, SCache master sets blocks of one round as the minimum unit of storage management.
We refer to this as the all-or-nothing constraint.
% According to all-or-nothing constraint, SCache master leverages the pre-scheduled results to determine the bound of each round, and sets blocks of one round as the minimum unit of storage management.
% For those incomplete units, SCache marks them as the lowest priority.

>>>>

% After a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API to move all the blocks out of framework worker through memory copy and release the slot immediately.
After a map task finishes computing, the shuffle writes in the map task is modified to use SCache API to memory copy all shuffle blocks to the SCache worker reserved memory.
% After that, the slot will be released (without being blocked on disk operations).
The SCache records the block ID and the size and sends them to the master.
% When a block of the map output is received, the SCache worker will send the block ID and the size to the master.
% If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
If the collected shuffle blocks reach a threshold, the SCache co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks.
After pre-scheduling, SCache workers start pre-fetching shuffle blocks according to the assignment from the master.
To enforce the DAG framework to assign tasks according to the SCache pre-scheduled results, we also insert some lines of codes in the framework scheduler.
}
% After modification, the DAG scheduler consults SCache co-scheduler to get the preferred location for each task.

@@

\subsubsection{All-or-Nothing Constraint}
% This acceleration of in-memory cache of a single task is necessary but insufficient for a shorter stage completion time. 
{\color{blue}
% Based on the observation in Section \ref{multi}, in most cases one single stage contains multi-rounds of tasks.
% Both experience and DAG framework manuals (e.g., Hadoop and Spark) recommend that multi-round execution of each stage will benefit the performance of applications.
As discussed in the observation in Subsection \ref{observation}, it is common to have multi-round execution of each stage. 
If one of the tasks in a round missed a memory cache, the re-fetch overhead will become a bottleneck and then slow down the whole stage. 
% If one task missed a memory cache and exceeded the original bottleneck of this round, that task might become the new bottleneck and then slow down the whole stage. 
% PACMan \cite{pacman} has also proved that for multi-round stage/job, the completion time improves in steps when $n\times number\ of\ tasks\ in\ one\ round$ of tasks have data cached simultaneously. 
% Therefore, the cached shuffle blocks need to match the demand of all tasks in one running round at least.
}
Therefore, SCache master sets blocks of one round as the minimum unit of storage management.
We refer to this as the all-or-nothing constraint.
% According to all-or-nothing constraint, SCache master leverages the pre-scheduled results to determine the bound of each round, and sets blocks of one round as the minimum unit of storage management.
% For those incomplete units, SCache marks them as the lowest priority.

### 2019-09-13 scache/tii/tex/model.tex
Revision

In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
% The FRQ model quantifies computing and I/O resources and visualizes them in the time dimension.
In the industrial production, the FRQ model is able to predict the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, etc.
% The FRQ model assist us in analyzing the resource scheduling of DAG framework and evaluate their performance.
We first introduce the FRQ model in Subsection \ref{model_overview}. In the following Subsection \ref{model_analysis}, we use the FRQ model to describe different computation jobs and discuss their performance.
% In the last Subsection \ref{model_evaluation}, we use the actual experimental results to evaluate the FRQ model.

\subsection{The FRQ Model}\label{model_overview}
% The current distributed computing frameworks mostly use DAGs to describe the computation logic. 
% A shuffle phase is required between each adjacent DAG computation phases.
{\color{blue}
We propose the FRQ model to better analyze the relationship between the computation phase and the shuffle phase in the DAG computing.
The FRQ model focuses on describing the overhead caused by the shuffle process.
This overhead does not only depends on the input data size, computation speed, complexity of algorithms, and other parameters but also on which scheduling strategy the job takes.
% By using the FRQ model, we can analyze the advantages of each strategy in various situations.
After quantifying computing and I/O resources, the FRQ model can evaluate different resource scheduling strategies by using different formulas.
% For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.

Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce job. 
As Figure \ref{fig:model_basic} shows, the FRQ model divides the job into three phases: map, shuffle, and reduce.
The horizontal axis represents time and the overlaps between phases represent they execute in parallel.
The FRQ model uses these overlaps to describe different scheduling strategies.
For example, as shown in Figure \ref{fig:model_hadoop}, this strategy starts the shuffle phase and the reduce phase at the same time.
And Figure \ref{fig:model_basic} shows the pre-fetching strategy used by SCache. In the pre-fetching strategy, the shuffle phase starts as soon as it can in the map phase.

% As shown in Figure \ref{fig:model_basic}, the FRQ model introduce five parameters:
Firstly, we introduce five input parameters of the FRQ model:
}
\begin{itemize}
	\item Input Data Size \((D)\): The  Input data size of the job.
	\item Data Conversion Rate \((R)\): The conversion rate of the input data to the shuffle data during a computation phase.
	% This rate depends on the algorithm used in the computation phase.
    \item Computation Round Number \((N)\): The number of rounds needed to complete the computation phase. These rounds depend on the current computation resources and the configuration of the framework. Take Hadoop MapReduce as an example. Suppose we have a cluster with 50 CPUs and enough memory, the map phase consists of 200 map tasks, and each map requires 1 CPU. Then we need 4 rounds of computation to complete the map phase.
    \item Computation Speed \((V_{i})\): 
	The computation speed for each computation phase.
	% This speed depends on the algorithm used in the computation phase.
    \item Shuffle Speed \((V_{Shuffle})\): 
	Transmission speed in the shuffle phase.
	% This speed depends on network and storage device bandwidth.
\end{itemize}

\begin{figure}
    \centering
	\includegraphics[width=\linewidth]{fig/model_basic}
	\caption{\color{black}Framework Resources Quantification Model\newline with Full Parallel MapReduce (\(V_{Map} \times R > V_{Shuffle}\))}
    \label{fig:model_basic}
    % \vspace{-1em}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/model_hadoop}
	\caption{\color{black}The FRQ Model with Half Parallel MapReduce}
	\label{fig:model_hadoop}
\end{figure}

@@

\subsection{Model Analysis}\label{model_analysis}

>>>>

In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to evaluate the performance of DAG frameworks.
% The FRQ model quantifies computing and I/O resources and visualizes them in the time dimension.
The FRQ model is able to predict the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, etc.
% The FRQ model assist us in analyzing the resource scheduling of DAG framework and evaluate their performance.
We first introduce the FRQ model in Subsection \ref{model_overview}. In Subsection \ref{model_analysis}, we use the FRQ model to describe different computation jobs and discuss their performance.
% In the last Subsection \ref{model_evaluation}, we use the actual experimental results to evaluate the FRQ model.

\subsection{The FRQ Model}\label{model_overview}
% The current distributed computing frameworks mostly use DAGs to describe the computation logic. 
% A shuffle phase is required between each adjacent DAG computation phases.
{\color{blue}
We propose the FRQ model to better analyze the relationship between the computation phase and the shuffle phase in the DAG computing.
% The FRQ model focuses on describing the overhead caused by the shuffle process.
The FRQ model focuses on describing the shuffle overhead which significantly effected by the scheduling strategy.
% This overhead does not only depends on the input data size, computation speed, complexity of algorithms, and other parameters but also on which scheduling strategy the job takes.
% By using the FRQ model, we can analyze the advantages of each strategy in various situations.
After quantifying computing and I/O resources, we use the FRQ model to evaluate different resource scheduling strategies.
% For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.

% Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce job. 
As Figure \ref{fig:model_basic} shows, the FRQ model divides the job into three phases: map, shuffle, and reduce.
The horizontal axis represents time and the vertical axis represents different phases.
% As shown in Figure \ref{fig:model_basic}, the FRQ model introduce five parameters:
Firstly, we introduce five input parameters of the FRQ model:
}
\begin{itemize}
	\item Input Data Size \((D)\): The  Input data size of the job.
	\item Data Conversion Rate \((R)\): The conversion rate of the input data to the shuffle data during a computation phase.
	% This rate depends on the algorithm used in the computation phase.
    \item Computation Round Number \((N)\): The number of rounds needed to complete the computation phase. These rounds depend on the current computation resources and the configuration of the framework. Take Hadoop MapReduce as an example. Suppose we have a cluster with 50 CPUs and enough memory, the map phase consists of 200 map tasks, and each map requires 1 CPU. Then we need 4 rounds of computation to complete the map phase.
    \item Computation Speed \((V_{i})\): 
	The computation speed for each computation phase.
	% This speed depends on the algorithm used in the computation phase.
    \item Shuffle Speed \((V_{Shuffle})\): 
	Transmission speed in the shuffle phase.
	% This speed depends on network and storage device bandwidth.
\end{itemize}

\begin{figure}
    \centering
	\includegraphics[width=\linewidth]{fig/model_basic}
	\caption{\color{black}Framework Resources Quantification Model\newline with Full Parallel MapReduce (\(V_{Map} \times R > V_{Shuffle}\))}
    \label{fig:model_basic}
    % \vspace{-1em}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/model_hadoop}
	\caption{\color{black}Framework Resources Quantification Model with Half Parallel MapReduce}
	\label{fig:model_hadoop}
\end{figure}

% The FRQ model uses these overlaps to describe different scheduling strategies.
{\color{blue}
Besides, the FRQ model also needs to input the scheduling strategies the framework takes.
The FRQ model needs to know the start time of each phases.
For example, as shown in Figure \ref{fig:model_hadoop}, this strategy starts the shuffle phase and the reduce phase at the same time.
And Figure \ref{fig:model_basic} shows the pre-fetching strategy used by SCache. In the pre-fetching strategy, the shuffle phase starts as soon as it can in the map phase.
}

@@

\subsection{Different Scheduling Strategies on the FRQ Model}\label{model_analysis}
